Notes on Hartree-Fock Stability of HEG

### 2017-04-08 doc/papers/workingequations/heg_equations.tex
Reorganized latex documents, each .tex gets its own directory !
Started some work on the summary
Added 1D support

\begin{subequations}
\begin{align}
\braket{\vec{k}, \vec{k}'|\vec{k}'',\vec{k}'''}\stackrel{\text{2D, 3D}}{=}&
	\begin{cases} 
	\frac{\pi}{\Omega}\frac{2^{D-1}}{|\vec{k}-\vec{k}''|^{D-1}} 
	& \vec{k}''' = \vec{k}+\vec{k}'-\vec{k}'' \textbf{ and } |\vec{k}-\vec{k}''| \neq 0 \\
	0 
	& \text{else}
	\end{cases}
\\ \nonumber \\
\braket{k, k'|k'',k'''}\stackrel{\text{1D}}{=}&
	\begin{cases} 
	e^{|k-k''|^2a^2}\text{Ei}(-|k-k''|^2a^2)\text{ ;}
	& k''' = k+k'-k'' \textbf{ and } |k-k''| \neq 0 \\
	0\text{ ;} 
	& \text{else}
	\end{cases}
\end{align}
\end{subequations}
where $\Omega$ is the direct lattice volume and D is the dimensionality of the system. Ei(x) denotes the exponential integral function. The orbital energies are given by

@@

\begin{equation}
(\epsilon_a-\epsilon_i)C_{ai}^* + \sum\limits_{\text{j}}^{occ}\sum\limits_{\text{b}}^{vir}
	(\braket{ij|ab}-\braket{ij|ba})C_{bj}
	+(\braket{ib|aj}-\braket{ib|ja})C_{bj}^*
	=\lambda C_{ai}^*,
\end{equation}
are nonnegative. This is equivalent to the RPA oscillation frequencies being all real (p. 115 of \cite{Thouless1972}). The RPA is a linearized approximation to Time-Dependent Hartree-Fock theory. These can be written\cite{Dunning1967}\cite{Seeger1977} in the following form:
\begin{equation}\label{eq:1,3H}
{}^{1,3}\bf{H'}=
\begin{bmatrix}
{}^{1,3}\bf{A'} & {}^{1,3}\bf{B'} \\
\left({}^{1,3}\bf{B'}\right)^* & \left({}^{1,3}\bf{A'}\right)^* \\
\end{bmatrix}
\end{equation}
Where the $1,3$ denote singlet and triplet states, respectively. $\bf{A}$, $\bf{B}$ have dimension $N_{occ}\times N_{vir}$ and are defined as follows:
\begin{subequations}
	\begin{align}
	{}^{1}{A'}_{i\rightarrow a, j\rightarrow b} &= (\epsilon_a-\epsilon_i)\delta_{ij}\delta_{ab} + 2\braket{aj|ib}-\braket{aj|bi}\\
	{}^{3}{A'}_{i\rightarrow a, j\rightarrow b} &= (\epsilon_a-\epsilon_i)\delta_{ij}\delta_{ab} - \braket{aj|bi}\\
	{}^{1}{B'}_{i\rightarrow a, j\rightarrow b} &= 2\braket{ab|ij}-\braket{ab|ji}\\
	{}^{3}{B'}_{i\rightarrow a, j\rightarrow b} &= -\braket{ab|ji}
	\end{align}
\end{subequations}
The matrix given in Equation \ref{eq:1,3H} represents the case of complex RHF stability in the space of complex RHF space (${}^{1}\mathbf{H}$ - internal instability) and in the space of complex UHF space (${}^{3}\mathbf{H}$ - triplet instability). Seeger and Pople \cite{Seeger1977} give both more general formulae, and simplifications in special cases. Figure \ref{fig:stability_table} is a reproduction of the stability conditions they developed, and more details can be found in the paper. 
\begin{figure}[h]
   \includegraphics[width=1.0\linewidth]{figures/seeger_stability.pdf}
  	\caption {Hartree-Fock Stability conditions reproduced from Seeger \& Pople \cite{Seeger1977}}
  	\label{fig:stability_table}
\end{figure}

@@

\subsection{Implementation}
\begin{algorithm}[H]
\caption{Davidson's Algorithm}\label{davidson}
\begin{algorithmic}[1]
\State create \bf{V}
\For {$i = 0, max\text{ }iterations$}
\State $\bf{\tilde{A}} = \bf{V}^\dag\bf{AV}$
\State $\tilde{\lambda},\mathbf{\tilde{x}} = eigensystem(\bf{\tilde{A}})$
\State sort $\tilde{\lambda},\mathbf{\tilde{x}}$
\If {$i > \textit{stringlen}$} \Return false
\EndIf
\State $j \gets \textit{patlen}$
\If {$\textit{string}(i) = \textit{path}(j)$}
\State $j \gets j-1$.
\State $i \gets i-1$.
\State \textbf{goto} \emph{loop}.
\State \textbf{close};
\EndIf
\State $i \gets i+\max(\textit{delta}_1(\textit{string}(i)),\textit{delta}_2(j))$.
\State \textbf{goto} \emph{top}.
\EndFor

\end{algorithmic}
\end{algorithm}

\section{Code Layout}
\begin{figure}[H]
   \includegraphics[width=1.0\linewidth]{figures/hf_stability_diagram.eps}
   \caption {Layout of code implementation. Red boxes are python, blue are C++ and purple dotted lines require cython. Green are likely to be removed for speed}
   \label{fig:code_diagram}
\end{figure}

>>>>

\begin{subequations}
\begin{align}
\braket{\vec{k}, \vec{k}'|\vec{k}'',\vec{k}'''}\stackrel{\text{2D, 3D}}{=}&
	\begin{cases} 
	\frac{\pi}{\Omega}\frac{2^{D-1}}{|\vec{k}-\vec{k}''|^{D-1}} 
	& \vec{k}''' = \vec{k}+\vec{k}'-\vec{k}'' \textbf{ and } |\vec{k}-\vec{k}''| \neq 0 \\
	0 
	& \text{else}
	\end{cases}
\\ \nonumber \\
\braket{k, k'|k'',k'''}\stackrel{\text{1D}}{=}&
	\begin{cases} 
	e^{|k-k''|^2a^2}\text{Ei}(-|k-k''|^2a^2)\text{ ;}
	& k''' = k+k'-k'' \textbf{ and } |k-k''| \neq 0 \\
	0\text{ ;} 
	& \text{else}
	\end{cases}
\end{align}
\end{subequations}
where $\Omega$ is the direct lattice volume and D is the dimensionality of the system. Ei(x) 
denotes the exponential integral function The parameter $a$ in 1D is the radius of a cylinder
that approximates a 1D system. The limit $a \rightarrow 0$ diverges. The orbital energies are given 
by

@@

\begin{equation}
(\epsilon_a-\epsilon_i)C_{ai}^* + \sum\limits_{\text{j}}^{occ}\sum\limits_{\text{b}}^{vir}
	(\braket{ij|ab}-\braket{ij|ba})C_{bj}
	+(\braket{ib|aj}-\braket{ib|ja})C_{bj}^*
	=\lambda C_{ai}^*,
\end{equation}
are nonnegative. This is equivalent to the RPA oscillation frequencies being all real (p. 115 of \cite{Thouless1972}). The RPA is a linearized approximation to Time-Dependent Hartree-Fock theory. These can be written\cite{Dunning1967}\cite{Seeger1977} in the following form:
\begin{equation}\label{eq:1,3H}
{}^{1,3}\bf{H'}=
\begin{bmatrix}
{}^{1,3}\bf{A'} & {}^{1,3}\bf{B'} \\
\left({}^{1,3}\bf{B'}\right)^* & \left({}^{1,3}\bf{A'}\right)^* \\
\end{bmatrix}
\end{equation}
Where the $1,3$ denote singlet and triplet states, respectively. $\bf{A}$, $\bf{B}$ have dimension $N_{occ}\times N_{vir}$ and are defined as follows:
\begin{subequations}
	\begin{align}
	{}^{1}{A'}_{i\rightarrow a, j\rightarrow b} &= (\epsilon_a-\epsilon_i)\delta_{ij}\delta_{ab} + 2\braket{aj|ib}-\braket{aj|bi}\\
	{}^{3}{A'}_{i\rightarrow a, j\rightarrow b} &= (\epsilon_a-\epsilon_i)\delta_{ij}\delta_{ab} - \braket{aj|bi}\\
	{}^{1}{B'}_{i\rightarrow a, j\rightarrow b} &= 2\braket{ab|ij}-\braket{ab|ji}\\
	{}^{3}{B'}_{i\rightarrow a, j\rightarrow b} &= -\braket{ab|ji}
	\end{align}
\end{subequations}
The matrix given in Equation \ref{eq:1,3H} represents the case of complex RHF stability in the space of complex RHF space (${}^{1}\mathbf{H}$ - internal instability) and in the space of complex UHF space (${}^{3}\mathbf{H}$ - triplet instability). Seeger and Pople \cite{Seeger1977} give both more general formulae, and simplifications in special cases. Figure \ref{fig:stability_table} is a reproduction of the stability conditions they developed, and more details can be found in the paper.

@@

\section{Code Layout}
\begin{figure}[H]
    TODO
\end{figure}
